\documentclass[windows]{BHCexam}
\usepackage{listings}

\begin{document}
\title{第四周复习}
\notice{建议30分钟内完成。}
\author{易翔}
\date{2021.3.27}

\maketitle

\group{判断题}{共3小题}
\begin{questions}[r]
\question Instance methods in a class can also be overloaded.\key{T}
\question \_\_gcd is a valid name of a variable.\key{T}
\question Static methods can be called without being instantiated.\key{T}
\end{questions}

\group{单项选择题}{共5小题}
\begin{questions}[pr]
\question Which of the following words is not a Java reserved word?\key{D}
\fourchoices{throw}{short}{extends}{instance}

\question Which of the following is NOT a valid way to declare an array?\key{C}
\fourchoices{int[] a = new int[12];}{char b[] = \{`1'\};}{long c[] = new long[2]\{1L, 3L\};}{boolean[] d; d = new boolean[2];}

\question What will the console output after executing the following statement?\key{D}\\
int t = 6;\\
System.out.print(t ++ + ++ t);
\fourchoices{Occur Compile Error}{12}{13}{14}

\question The following is part of the code in the program. Which line of the statement will report a runtime error?\key{D}\\
byte i = 5;\\
System.out.print((int) i);\\
i = i + 1;
\fourchoices{There is no error.}{Line 1}{Line 2}{Line 3}
\question What will the console output after executing the following statement?\key{C}\\
char[] chars = new char[]\{`1', `2', `3'\};\\
System.out.println(chars);
\fourchoices{Occur Compile Error}{Out-put the address of the array}{123}{[`1', `2', `3']}
\end{questions}

\group{简答题}{共1小题}
\begin{questions}[t]
\question Now you are ask to recursively(递归地) approach a method to calculate factorial(阶乘) of a nonnegative integer n.

public static int factorial (int n) \{\\
	\text{ }\quad\quad// implement your code here.\\
\}
\key{略}
\end{questions}
\end{document}
